Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-06 trunk/paper.tex

The major system parameter to be reconfigured is the capacity of each memory
level. At each time interval, we determine the upper bound of the capacity of
memory level-i ($s_{iu}$) by mapping the demand bandwidth (DBW) of a specific
application to the system's provided bandwidth curve, i.e.,
$s_{iu}=f^{-1}(\textrm{DBW})$ where $f(x)$ represents the provided bandwidth
curve of the on-chip memory system stored in the look-up-table in a reserved
non-volatile memory space. The demand bandwidth for each memory level is
generated using the prediction engine presented in section~\ref{sec:predict}. In
previous sections, we show that the memory with smaller capacity provides higher
bandwidth. Theoritically, the higher bandwidth provided by the memory system
leads to higher performance (in terms of throughput) and power consumption of
throughput computing applications~\cite{throughput-vs-bandwidth}. Consequently,
we define a lower bound of memory capacity as
$s_{il}=f^{-1}(\textrm{DBW}*(1+\sigma))$, where $\sigma$ is a pre-defined
threshold to make sure possible provided bandwidth increase without much power
overhead. The capacity of memory level-i ($s_i$) is therefore selected to
satisfy $s_{il}\le s_i\le s_{iu}$. Furthermore, the rest of the capacity can be
reconfigured to become level-i.5 if necessary. We describe the reconfiguration
algorithm as follows.

>>>>

The major system parameter to be reconfigured is the capacity of each memory
level. At each time interval, we determine the upper bound of the capacity of
memory level-i ($s_i^u$) by mapping the demand bandwidth (DBW) of a specific
application to the system's provided bandwidth curve, i.e.,
$s_i^u=f^{-1}(\textrm{DBW})$ where $f(x)$ represents the provided bandwidth
curve of the on-chip memory system stored in the look-up-table in a reserved
non-volatile memory space. The demand bandwidth for each memory level is
generated using the prediction engine presented in section~\ref{sec:predict}. In
previous sections, we show that the memory with smaller capacity provides higher
bandwidth. Theoritically, the higher bandwidth provided by the memory system
leads to higher performance (in terms of throughput) and power consumption of
throughput computing applications~\cite{throughput-vs-bandwidth}. Consequently,
we define a lower bound of memory capacity as
$s_i^l=f^{-1}(\textrm{DBW}*(1+\sigma))$, where $\sigma$ is a pre-defined
threshold to make sure possible provided bandwidth increase without much power
overhead. The capacity of memory level-i ($s_i$) is therefore selected to
satisfy $s_i^l\le s_i\le s_i^u$. Furthermore, the rest of the capacity can be
reconfigured to become level-i.5 if necessary. We describe the reconfiguration
algorithm as follows.
